---
title: "Quantifying community and environmental drivers of resilience in GoM fisheries"
output: html_document
---


```{r init, echo = FALSE, warning=FALSE, message=FALSE}
here::i_am("doc/pre-proposal.Rmd")
knitr::opts_chunk$set(echo =FALSE, message = FALSE, warning = FALSE)
# load libraries
library(tidyverse)
library(arrow)
library(here)
library(googleCloudStorageR)
library(leaflet)
library(viridis)

theme_set(theme_minimal())
# Load in data
## set the location to the GCS bucket
ldwfBucket <- arrow::gs_bucket("ldwf_data", json_credentials = readr::read_file(Sys.getenv('GCS_AUTH_FILE')))

## open the dataset 
ldwfData = open_dataset(
  sources = ldwfBucket
  )

## get and set station latlongs
ldwfStationLatLong = ldwfData %>% 
  select(station, latitude, longitude) %>% 
  group_by(station, latitude, longitude) %>% 
  summarise(n = n()) %>% 
  group_by(station) %>% 
  collect() %>% 
  slice_max(n) %>% 
  filter(station != 8888)


## subset the database by station
ldwfStationSumm = ldwfData %>% 
  select(station, date, gear) %>% 
  collect() %>% 
  separate_wider_position(date, widths = c(year = 4, month = 2, day = 2)) %>%
  tidyr::unite("date", year:day, sep = "-") %>% 
  mutate(date = as.Date(date, format = "%Y-%m-%d")) %>% 
  unique() %>% 
  group_by(station, gear) %>% 
  summarise(samples = n()) %>% 
  filter(station != 8888) %>% 
  left_join(ldwfStationLatLong, by = "station") %>% 
  filter(longitude != 0)

```

Questions of interest:

- How does resilience in ecological communities (i.e., fishes, nekton) change over time and space?

- What is the spatial response of communities to local and regional pulse or press disturbances?

- 

Potential data sources:

- state-based fisheries-inependent monitoring data. LDWF monitoring data outlined here as an example






Details of submission:

- Due date: May 23, 2024


# Initial data availability

```{r gear maps, fig.height=5, fig.width=7, fig.cap="Preliminary assessment of unique samples in LA DWF fisheries-independent sampling. *This data only goes until 2019."}
# get map base
LA_map = map_data('state', region = 'Louisiana')

LA_map %>% 
ggplot() +
  geom_polygon(aes(long, lat), fill = NA, color = 'black')+
  coord_sf()+
  geom_point(data = ldwfStationSumm %>% mutate(gear = as.character(gear)), aes(x =longitude, y = latitude, size = log10(samples), fill = gear), alpha = 0.5, shape = 21) +
  guides(fill = 'none')+
  scale_y_continuous(limits = c(NA, 31))+
  scale_color_viridis(discrete = TRUE)

```

## Example community data

```{r station 1000 summary}
summ1000 = ldwfData %>% 
  select(special, date, station, len_int, len_m, len_m_description, t_num, common_name, gear_desc, num_meas) %>%
  filter(station == 1000) %>% 
  collect() %>% 
  separate_wider_position(date, widths = c(year = 4, month = 2, day = 2)) %>%
  tidyr::unite("date", year:day, sep = "-") %>% 
  mutate(date = as.Date(date, format = "%Y-%m-%d"))



```