---
title: "Quantifying community and environmental drivers of resilience in GoM fisheries"
output: html_document
---

```{r init, echo = FALSE, warning=FALSE, message=FALSE}
here::i_am("doc/pre-proposal.Rmd")
knitr::opts_chunk$set(echo =FALSE, message = FALSE, warning = FALSE)
# load libraries
library(tidyverse)
library(arrow)
library(here)
library(googleCloudStorageR)
library(leaflet)
library(viridis)
library(vegan)

options(mc.cores = parallel::detectCores())
theme_set(theme_minimal())
# Load in data
## set the location to the GCS bucket
ldwfBucket <- arrow::gs_bucket("ldwf_data", json_credentials = readr::read_file(Sys.getenv('GCS_AUTH_FILE')))

## open the dataset 
ldwfData = open_dataset(
  sources = ldwfBucket
  )

## get and set station latlongs
ldwfStationLatLong = ldwfData %>% 
  select(station, latitude, longitude) %>% 
  group_by(station, latitude, longitude) %>% 
  summarise(n = n()) %>% 
  group_by(station) %>% 
  collect() %>% 
  slice_max(n) %>% 
  filter(station != 8888)


## subset the database by station
ldwfStationSumm = ldwfData %>% 
  select(station, date, gear) %>% 
  collect() %>% 
  separate_wider_position(date, widths = c(year = 4, month = 2, day = 2)) %>%
  tidyr::unite("date", year:day, sep = "-") %>% 
  mutate(date = as.Date(date, format = "%Y-%m-%d")) %>% 
  unique() %>% 
  group_by(station, gear) %>% 
  summarise(samples = n()) %>% 
  filter(station != 8888) %>% 
  left_join(ldwfStationLatLong, by = "station") %>% 
  filter(longitude != 0)

```

Questions of interest:

- How does resilience in ecological communities (i.e., fishes, nekton) change over time and space?

- What is the spatial response of communities to local and regional pulse or press disturbances?

- 

Potential data sources:

- state-based fisheries-independent monitoring data. LDWF monitoring data outlined here as an example






Details of submission:

- Due date: May 23, 2024


# Initial data availability

```{r gear maps, fig.height=5, fig.width=7, fig.cap="Preliminary assessment of unique samples in LA DWF fisheries-independent sampling. Dots are scaled in size by the number of individual sample dates present in the data set and the fill color represents the gear type. The large red dot represents a single station whose dynamics are highlighted below. *This data only goes until 2019 and coordinate system has not been confirmed for exact locations."}
# get map base
LA_map = map_data('state', region = 'Louisiana')
# summarise a single site
summ1000 = ldwfData %>% 
  select(special, date, station, len_int, len_m, len_m_description, t_num, common_name, gear_desc, num_meas) %>%
  filter(station == 1000) %>% 
  collect() %>% 
  separate_wider_position(date, widths = c(year = 4, month = 2, day = 2)) %>%
  tidyr::unite("date", year:day, sep = "-") %>% 
  mutate(date = as.Date(date, format = "%Y-%m-%d"))

LA_map %>% 
ggplot() +
  geom_polygon(aes(long, lat), fill = NA, color = 'black')+
  coord_sf()+
  geom_point(data = ldwfStationSumm %>% mutate(gear = as.character(gear)), aes(x =longitude, y = latitude, size = log10(samples), fill = gear), alpha = 0.5, shape = 21) +
  geom_point(data = ldwfStationSumm %>% filter(station == 1000), aes(x =longitude, y = latitude), color = 'red', shape = 21, fill = 'white', size = 5, stroke = 1.1) +
  guides(fill = 'none')+
  # scale_y_continuous(limits = c(NA, 32))+
  coord_cartesian(ylim = c(NA, 32))+
  scale_color_viridis(discrete = TRUE)

```

## Example community data

```{r station 1000 summary}

comm1000 = summ1000 %>% 
  group_by(date, common_name) %>% 
  summarise(num_meas = sum(num_meas, na.rm = TRUE))

comm1000_catch = comm1000 %>% 
  group_by(common_name) %>% 
  mutate(pres = ifelse(num_meas >0, 1,0))

comm1000_presWide = comm1000_catch %>% 
  ungroup %>%
  select(-num_meas) %>% 
  pivot_wider(names_from = 'common_name', values_from = 'pres', values_fill = 0)

comm1000_wide = comm1000 %>% 
  pivot_wider(names_from = 'common_name', values_from = 'num_meas', values_fill = 0) %>% 
  ungroup %>% 
  select(-date) %>% 
  filter(rowSums(.)>0)

comm1000_dom = comm1000 %>% 
  ungroup %>% 
  group_by(common_name) %>% 
  summarise(num_meas = sum(num_meas)) %>% 
  mutate(rel_n = num_meas/sum(num_meas))

comm1000_domVec = comm1000_dom %>% 
  arrange(desc(rel_n)) %>%
  slice(1:7) %>%
  select(common_name) %>%
  unlist

comm1000_domScaled = comm1000 %>% 
  filter(common_name %in% comm1000_domVec) %>% 
  pivot_wider(names_from = 'common_name', values_from = 'num_meas', values_fill = 0) %>% 
  ungroup %>% 
  mutate(across(where(is.numeric), scale)) %>% 
  pivot_longer(-date, names_to = 'common_name', values_to ='n_scaled')

comm1000_domScaled %>% 
  ggplot()+
  geom_point(aes(x = date, y = n_scaled, color = common_name))+
  geom_path(aes(x = date, y = n_scaled, color = common_name))+
  scale_color_viridis(discrete = TRUE)+
  coord_cartesian(ylim = c(0, 10))+
  facet_wrap(~common_name, scales = 'free_y')

# dist1000_bc = vegdist(comm1000, method = 'bray')
# conn1000_bc = distconnected(dist1000_bc, toolong = 0.9)
# comm1000_mod = comm1000[which(conn1000_bc == 1),]
# 
# rerun = TRUE
# if(rerun){
# set.seed(1312)
# nmds1000 = metaMDS(comm = comm1000, k = 2, autotransform = TRUE,
#                    noshare = TRUE, parallel = 12,
#                    try = 30, trymax = 100,maxit = 500,
#                    sfgrmin = 1e-9, sratmax= 0.99999,
#                    tidy = TRUE)
# nmds1000.2 = metaMDS(comm = comm1000_mod,previous.best = nmds1000, parallel = 12)
# saveRDS(nmds1000.2, here::here("data/nmds1000.rds"))
# } else{
#   nmds1000 = readRDS(here::here("data/nmds1000.rds"))
# }
# 
#  plot(nmds1000.2)

```
